Where and Why Do Models Fail? A Visualization Tool for Analyzing and Interpreting Natural Language Inference

### 2018-03-03 paper/background.tex
fix resizing

Recently, with the wide adoption of long-short term memory
(LSTM) network and the introduction of attention mechanism,
neural network based model have
dominated nearly all linguistic tasks and thoroughtly refreshed the
baseline performances.
%
However, the disruptive advance also brings enormous challenges.
Due to the opaque nature of the neural network model, interpret and making sense
of many internal model mechanisms can be extremely challenging.
%
Many methods has been proprosed

The discrete nature of words and
sentences presents additional challenge for make sense of the model.
%

\subsection{Textual Entailment Problem}

\begin{itemize}
    \item what is the textaul entailment problem
    \item the importance of textual entailment problem
    \item how easily can the visualization method extends other NLP problem
\end{itemize}

@@

\subsection{Interprebilty Challenges}

>>>>

\begin{itemize}
    \item Motivation for TE: reading comprehension, similarity of senten ce
    \item what is it?
    \item its connection with other NLP tasks (one of the key)
    \item
\end{itemize}

The grand challenge in natural language processing (NLP) such as
machine reading require a deeper understanding the

% Recently, with the wide adoption of long-short term memory
% (LSTM) network and the introduction of attention mechanism,
% neural network based model have dominated nearly all linguistic tasks
% and thoroughtly refreshed many baseline performances.
% %
% However, the disruptive advance also brings enormous challenges.
% Netural network work based on has long been critizied for their opaque nature,
% and often been regarded as back box approach.
% Due to the opaque nature of the neural network model, interpret and making sense
% of many internal model mechanisms can be extremely challenging.

The discrete nature of words and sentences presents additional challenge for
interpreting the model, since many visualization technique often employed
for images rely on continues nature of the input space (e.g., one can interpolate
real values much easier than interplolate between words/sentences).
%

% \subsection{Natural Language Inference}

% \begin{itemize}
%     \item what is the textaul entailment problem
%     \item the importance of textual entailment problem
%     \item how easily can the visualization method extends other NLP problem
% \end{itemize}

@@

% \subsection{Interprebilty Challenges}

### 2018-03-03 paper/intro.tex
fix resizing

% (What is the high level motivation)
% What is the obsatcle for effectively apply machine learning model
With the recent advances in neural network based model, machine learning has
gained unprecedented popularity, and its adaption permeated many fields of studies.
%
However, from researchers to practitioners, one often need to overcome many
obstacles during the training, debugging, and tuning processes to unleash
the full potential of these models.
%
Identify where and how does the error occur and understand why does the model
fail is critical to the design and application of various models.
%quickly identify where the errors are
However, providing meaningful answers to these questions is an extremely challenging task.
% Naturally the identification of failure scenarios is an essential first step in diagnosing procedure.
%the potential limitation of the test dataset
On the one hand, the standard evaluation approach provides limited information. The performance number (i.e., prediction accuracy on the test set) alone often cannot answer many important questions for the model diagnostic process. Understanding what the often made mistakes are, and how sensitive are the model concerning perturbation in the input, etc., are instrumental. On the other hand, understanding why the model fails is challenging as well, which undoubtedly will require the ability to peek inside the model and make sense of the critical internal mechanisms.

@@

In this work, we introduce a visualization system that through a tight yet flexible integration between visual analytic elements and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
We use textual entailment task~\cite{BowmanAngeliPotts2015} as an example to illustrate how this system help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model and probe the inner states of the model for interpreting key mechanism such as attention.

@@

    \item Enable the interrogation of the attention mechanism by interactively exploring how the change in prediction affect the attention and vice versa while fixing other part of the model

>>>>

% (What is the high level motivation)
% What is the obsatcle for effectively apply machine learning model
With the recent advances in neural network based model, machine learning has
gained unprecedented popularity, and its adaption permeated many fields of studies.
%
However, from researchers to practitioners, one often need to overcome many
obstacles during the training, debugging, and tuning processes to unleash
the full potential of these models.
%
Identify where and how does the error occur and come up with hypothesis for
why does the model fail is critical to the design and application of various models.
%quickly identify where the errors are
However, providing meaningful answers to these questions is an extremely challenging task.
% Naturally the identification of failure scenarios is an essential first step in diagnosing procedure.
%the potential limitation of the test dataset
On the one hand, the standard evaluation approach provides limited information. The performance number (i.e., prediction accuracy on the test set) alone often cannot answer many important questions in the model diagnostic process. Understanding what the often made mistakes are, and how sensitive are the model concerning perturbation in the input, etc., are instrumental. On the other hand, infer why the model fails is challenging as well (i.e., models are often referred to as black boxes),
which require the ability to peek inside the model and understand the relationship between the
model input, critical internal mechanisms, as well the output predictions.

@@

In this work, we introduce a visualization system that through a tight yet flexible integration between visual analytic elements and the underlying model, allow a user to interrogate the model by perturbing the input, the internal state, as well as prediction while observing changes in other parts of the pipeline.
We use textual entailment task~\cite{BowmanAngeliPotts2015} as an example to illustrate how this system help natural language processing (NLP) researchers quickly identify the potential limitation of an NLP model, probe the inner states of the model for interpreting key mechanism such as attention, and ultimately come up with hypothesis on why the model fails.

@@

    \item Enable the interrogation of the relationship between input sentences, attention, and the prediction by interactively exploring how the change in one of these elements affect other parts of the model.

### 2018-03-03 paper/perturbation.tex
fix resizing

\subsection{Input Perturbation}
Iterate the model design and debug the system hinged on the ability to quickly and identify the errors made by a model.

>>>>

\subsection{Input Perturbation}
\begin{itemize}
    \item Just looking at the failure cases is not enough, the prediction maybe correct for the wrong reason
    \item sensitivity of the model with respect of
\end{itemize}

Iterate the model design and debug the system hinged on the ability to quickly and identify the errors made by a model.
